\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web

### 2020-03-23 revision3_2581/paper.tex
added authorship

\author{Eduard Sz\"ocs\\Universit\"at Koblenz-Landau \And
	Tam\'as Stirling\\Independent Developer \And
        Ralf B. Sch\"afer\\Universit\"at Koblenz-Landau}
\title{\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web}

\Plainauthor{Eduard Sz\"ocs, Tam\'as Stirling, Ralf B. Sch\"afer}

>>>>

\author{Eduard Sz\"ocs\\Universit\"at Koblenz-Landau \And
	      Tam\'as Stirling\\Independent Developer \And
	      Andreas Scharm\"uller\\Universit\"at Koblenz-Landau \And
        Ralf B. Sch\"afer\\Universit\"at Koblenz-Landau}
\title{\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web}

\Plainauthor{Eduard Sz\"ocs, Tam\'as Stirling, Andreas Scharm\"uller, Ralf B. Sch\"afer}
